### 2022-10-14 doc/manuscript/translocation.qmd
Quarto reformatting
Add manuscript formatting guidance

@@

### Abstract:

### One Sentence Summary

### Main Text:

@@

@@

@@

@@

<!--# Mention declining populations also? -->

@@

### References and Notes:

### Acknowledgements:

\#### Funding

\#### Author contributions:

\#### Competing interests:

\#### Data and materials availability

### Supplementary Materials:

### Fig. #.

### Table #.

>>>>

<!--# 75 characters. Suggestions to make this more compelling? Use "Evolutionary rescue"? -->

@@

### Abstract

<!--# No more than 200 words, follow structure described in instructions for authors. 2-3 sentences of basic-level introduction to the field; a brief account of the background and rationale of the work; a statement of the main conclusions (introduced by the phrase 'Here we show' or its equivalent);
 and finally, 2-3 sentences putting the main findings into general context so it is clear how the results described in the paper have moved the field forwards. See [annotated example](https://www.nature.com/documents/nature-summary-paragraph.pdf).  -->

### Main

<!--# subheadings can be used, can be "teasers" of results (up to 40 characters) -->

@@

### Figures and figure legends

<!--# In initial submission, include figure legends with their corresponding figures. -->

@@

<!--# Typically less than 3000 words -->

@@

<!--# subheadings can be used, up to 40 characters -->

<!--# Mention sampled declining populations also? -->

@@

@@

### References

### Acknowledgements

### Author contributions

### Competing interests statement

### Additional information

Supplementary Information is available for this paper.

Correspondence and requests for materials should be addressed to Roland Knapp.

Peer review information.

Reprints and permissions information is available at www.nature.com/reprints.

### Supplementary Information
